## **Problem**

A [**string**](https://rosalind.info/glossary/string/) is simply an ordered collection of symbols selected from some [**alphabet**](https://rosalind.info/glossary/alphabet/) and formed into a word; the [**length**](https://rosalind.info/glossary/string-length/) of a string is the number of symbols that it contains.

An example of a length 21 [**DNA string**](https://rosalind.info/glossary/dna-string/) (whose alphabet contains the symbols 'A', 'C', 'G', and 'T') is "ATGCTTCAGAAAGGTCTTACG."

**Given:** A DNA string s of length at most 1000 nt.

**Return:** Four integers (separated by spaces) counting the respective number of times that the symbols 'A', 'C', 'G', and 'T' occur in s.

## **Sample Dataset**

```{r}
s <- 'AGCTTTTCATTCTGACTGCAACGGGCAATATGTCTCTGTGTGGATTAAAAAAAGAGTGTCTGATAGCAGC'
```

## **Sample Output**

```         
20 12 17 21
```

```{r}
count_nucleotides <- function(f){
  #we want to count each of the occurrences for each respective nucleotides in our DNA string s
  countA <- sum(strsplit(s, NULL)[[1]] == "A")
  countC <- sum(strsplit(s, NULL)[[1]] == "C")
  countT <- sum(strsplit(s, NULL)[[1]] == "T")
  countG <- sum(strsplit(s, NULL)[[1]] == "G")
  return(c(countA, countG, countT, countC))
}

nucleotides <- count_nucleotides(s)
#print(nucleotides)
cat(nucleotides, sep = " ")
```
